\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Updated Figure 13 title (Need to record videos)

```{r}
#| label: fig-five-gau-projs
#| fig-height: 15
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "Model in \\gD{}, on the layouts from tSNE, UMAP, and PaCMAP (a1, b1, c1). Two views of the fit in projections of each layout from $4\\text{-}D$, for the Gaussian cluster data. All \\gD{} models show five well-separated clusters with different gaps. Layout a1 shows small separations, while layout b2 shows large gaps. On the other hand, layout b3 shows average gaps with exact positions as in $4\\text{-}D$. Assessing the different models fit for different layouts for a specific cluster shows filled-out shape in a1, a2, and b1, b2. On the other hand, c1 and c2 shows pancake shape.  The full video for the model for layout a, b, and c are available at <https://youtu.be/5Y1hE4i7N2k>, <https://youtu.be/5Y1hE4i7N2k>, and <https://youtu.be/5Y1hE4i7N2k> respectively."

>>>>

```{r}
#| label: fig-five-gau-projs
#| fig-height: 15
#| fig-width: 15
#| fig-pos: H
#| fig-cap: "Model in \\gD{}, on the layouts a1, b1, and c1, and two views of the fit in projections of each layout from $4\\text{-}D$, for the five Gaussian cluster data. All \\gD{} models show five well-separated clusters with different gaps. Layout a1 shows small separations, while layout b2 shows large gaps. On the other hand, layout b3 shows average gaps with exact positions as in $4\\text{-}D$. Assessing the different models fit for different layouts for a specific cluster (highlighted in red) shows filled-out shape in a1, a2, and b1, b2. On the other hand, c1 and c2 shows pancake shape.  Videos of the langevitour animations are available at <https://youtu.be/5Y1hE4i7N2k>, <https://youtu.be/5Y1hE4i7N2k>, and <https://youtu.be/5Y1hE4i7N2k> respectively."

### 2024-09-26 paper.tex
Updated Figure 13 title (Need to record videos)

\caption{\label{fig-five-gau-projs}Model in \gD{}, on the layouts from
tSNE, UMAP, and PaCMAP (a1, b1, c1). Two views of the fit in projections
of each layout from \(4\text{-}D\), for the Gaussian cluster data. All
\gD{} models show five well-separated clusters with different gaps.
Layout a1 shows small separations, while layout b2 shows large gaps. On
the other hand, layout b3 shows average gaps with exact positions as in
\(4\text{-}D\). Assessing the different models fit for different layouts
for a specific cluster shows filled-out shape in a1, a2, and b1, b2. On
the other hand, c1 and c2 shows pancake shape. The full video for the
model for layout a, b, and c are available at
\url{https://youtu.be/5Y1hE4i7N2k}, \url{https://youtu.be/5Y1hE4i7N2k},
and \url{https://youtu.be/5Y1hE4i7N2k} respectively.}

>>>>

\caption{\label{fig-five-gau-projs}Model in \gD{}, on the layouts a1,
b1, and c1, and two views of the fit in projections of each layout from
\(4\text{-}D\), for the five Gaussian cluster data. All \gD{} models
show five well-separated clusters with different gaps. Layout a1 shows
small separations, while layout b2 shows large gaps. On the other hand,
layout b3 shows average gaps with exact positions as in \(4\text{-}D\).
Assessing the different models fit for different layouts for a specific
cluster (highlighted in red) shows filled-out shape in a1, a2, and b1,
b2. On the other hand, c1 and c2 shows pancake shape. Videos of the
langevitour animations are available at
\url{https://youtu.be/5Y1hE4i7N2k}, \url{https://youtu.be/5Y1hE4i7N2k},
and \url{https://youtu.be/5Y1hE4i7N2k} respectively.}
